---
title: "Run the targets plan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run the targets plan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```
1. This workflow requires file inputs to be stored on [Synapse](https://www.synapse.org). It is free to make an account and store
small files. Store your counts files and metadata on Synapse.

2. [Write your own config file](https://sage-bionetworks.github.io/sageseqr/articles/customize-config.html).

3. Specify the active configuration by setting `R_CONFIG_ACTIVE`.

```{r config-setup}
profile_set <- "default"
Sys.setenv(R_CONFIG_ACTIVE = profile_set)
```

4. Store your Synapse credentials locally. You can achieve this by either creating a  `.synapseConfig` file or executing `synLogin()` with `rememberMe = True`. [This article](https://r-docs.synapse.org/articles/manageSynapseCredentials.html) provides more context to storing Synapse credentials.

5. Load the `sageseqr` library. `start_de()` copies the `targets` plan to your working directory. Execute `targets::make()` to compute. Run this code from your project root.

```{r run-plan}
library(sageseqr)
# gather the dependencies in your working directory by running this function:
start_de()
# inspect the steps of the workflow
targets::tar_manifest()
# run the analysis
targets::tar_make()
```

4. Visualize the results of your work. 

```{r visualize}
targets::tar_glimpse(
  targets_only = TRUE
)
```
