---
title: "Run the drake plan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run the drake plan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

1. [Write your own config file](https://kelshmo.github.io/sageseqr/articles/customize-config.html).

2. Specify the active configuration by setting `R_CONFIG_ACTIVE`.

```{r config-setup}
Sys.setenv(R_CONFIG_ACTIVE = "default")
```

3. Load the `sageseqr` library and login to [Synapse](https://www.synapse.org/). `rnaseq_plan()` calls the arguments from the config file and creates the `drake` plan. Execute `drake::make(plan)` to compute. It is required to explicitly specify the name of the cache created with `drake::new_cache()` when multiple plans are executed in the same R session. Run this code from your project root.

```{r run-plan}
library(sageseqr)

# Login to Synapse. Make a Synapse account and use synapser to login: https://r-docs.synapse.org/articles/manageSynapseCredentials.html
synapser::synLogin()

# Run the analysis
plan <- sageseqr::rnaseq_plan(
  metadata_id = config::get("metadata")$synID,
  metadata_version = config::get("metadata")$version,
  counts_id = config::get("counts")$synID,
  counts_version = config::get("counts")$version,
  gene_id_input = config::get("counts")$`gene id`,
  sample_id_input = config::get("metadata")$`sample id`,
  factor_input = config::get("factors"),
  continuous_input = config::get("continuous"),
  biomart_id = config::get("biomart")$synID,
  biomart_version = config::get("biomart")$version,
  filters = config::get("biomart")$filters,
  host = config::get("biomart")$host,
  organism = config::get("biomart")$organism, 
  conditions = config::get("conditions"), 
  x_var_for_plot = config::get("x_var"), 
  sex_var = config::get("sex check"), 
  color = config::get("dimensions")$color, 
  shape = config::get("dimensions")$shape,
  size = config::get("dimensions")$size,
  report_name = config::get("report"),
  skip_model = config::get("skip model"),
  parent_id = config::get("store output"),
  rownames = list(
    config::get("counts")$`gene id`, 
    config::get("metadata")$`sample id`,
    config::get("counts")$`gene id`,
    config::get("biomart results")$filters
    ),
  config_file = "config.yml",
  path_to_cache = config::get("analysis title")
)

drake::make(
  plan,
  cache = drake::new_cache(
    config::get(
      "analysis title"
      )
    )
  )
```

4. Visualize the results of your work. 

```{r visualize}
drake::vis_drake_graph(
  plan,
  targets_only = TRUE
  )
```
