---
date: "`r date()`"
output: 
  html_document:
    css: style.css
    toc: true
    toc_float: true
---
```{r title}
project <- config::get("analysis title")
```
---
title: `r project`
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      fig.align = 'left',
                      fig.width = 10, 
                      fig.height = 10)
library(sageseqr)
```
# Data


# Explore Metadata

```{r sample_summary, message = FALSE}
drake::loadd(clean_md)
var <- config::get("x_var")
summary <- dplyr::group_by_at(clean_md, var)
summary <- dplyr::summarise(summary, count = dplyr::n())
knitr::kable(summary)
```

Visualize the distribution of data.
```{r boxplot}
drake::readd(boxplots)
```

```{r boxplot_sex_chromosomes, results = "asis"}
if (!is.null(config::get("sex check"))) {
  cat("Visualize gene expression of sex chromosomes using XIST 
      as a X-chromosome marker and UTY as a Y-chromosome marker.")
  drake::readd(sex_plot)$plot
   cat("Visualize gene expression across X and Y chromosomes by principal component analysis (PCA).")
   drake::readd(sex_plot_pca)$plot
}
```
Possible outliers, identified as 2 standard deviations from the mean of samples n split by `r config::get("sex check")`, are `r glue::glue_collapse(drake::readd(sex_plot_pca)$outliers, ", ", last = " and ")`.

Visualize the relationships between covariates.
```{r heatmap_covariates}
correlation_input <- drake::readd(
  correlation_plot
  )$plot
col2 <- grDevices::colorRampPalette(rev(c("#67001F", "#B2182B", "#D6604D", "#F4A582",
                                 "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                                 "#4393C3", "#2166AC", "#053061")))
corrplot::corrplot(correlation_input, col = col2(200), tl.col = "#000000")
```

# Filter Genes

Remove genes that have less than 1 counts per million (CPM) in at least 50% of samples per specified condition.

`r dim(drake::readd(filtered_counts))[1]` genes are used in this analysis.
```{r filter_genes}
knitr::kable(drake::readd(biotypes))
```

Check distribution of correlation between genes.
```{r histogram}
drake::readd(gene_coexpression)
```

# Identify Outliers

```{r plot_outliers}
drake::readd(outliers)$plot
```
Outliers, based on logCPM expression, are `r glue::glue_collapse(drake::readd(outliers)$outliers, ", ", last = " and ")`.

# Significant Covariates

Significant covariates are identified by the pearson correlation (p-value of 1%) between principal component analysis (PCA) of normalized transcripts and variables that meet a 0.1 false discovery rate (FDR) threshold. Significant covariates to adjust for are `r glue::glue_collapse(drake::readd(significant_covariates_plot)$significant_covariates, ", ", last = " and ")`.

```{r pca_and_significant_covariates}
drake::readd(
  significant_covariates_plot
  )$plot
```

```{r model}
if (!isTRUE(config::get("skip model"))) {
  cat("# Model Identification
Covariates are added as fixed and random effects iteratively if model improvement by  Bayesian Information Criteria (BIC) was observed.")

summary <- drake::readd(model)
knitr::kable(summary$to_visualize)
as.character(summary$formula)[2]
}
```
